%------------------------
% Resume Template
% Author : Jai Agarwal
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\projectSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Jai Agarwal}} & Email: \href{mailto:jai.bhageria@gmail.com}{jai.bhageria@gmail.com} \\

  \faGithub \href{https://github.com/jaibhageria}{ Github~~~: \color{blue}https://github.com/jaibhageria} & Mobile:~~~+91-966-3506-821~~~~~~\\
  \faLinkedin \href{https://linkedin.com/in/jai-bhageria}{ LinkedIn~: \color{blue}https://linkedin.com/in/jai-bhageria} \\
   \faGlobe \href{https://jaib.home.blog}{ Website~~: \color{blue}https://jaib.home.blog} \\
   \faIcon{graduation-cap}\color{blue}\href{https://scholar.google.com/citations?user=ENPIQwEAAAAJ&hl=en}{ Google Scholar account} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{\faIcon{book}~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PES University}{Bangalore, India}
      {Bachelor of Technology - Computer Science and Engineering}{August 2016 - July 2020}
      {\textit{{\newline{}\newline{}\textbf{GPA: 9.48/10}{; Graduated First Class with Distinction \footnotesize{\faIcon{link}} \color{blue}\small\href{https://bit.ly/3FIEsQN}{Transcript}}}}}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:}  Data Structures \& Algorithms, Operating Systems, Big Data \& Cloud Computing, Cloud Computing, Computer Networks \&
Security, Objected Oriented Design, Web Technologies - I \& II, Data Analytics, Machine Learning, Deep Learning.}}}
    \resumeSubHeadingListEnd

\vspace{-5pt}
\section{\faIcon{server}~~Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Strengths}{~~~~~~~~~~~ Strong programming \& debugging ability, Web Development, Application Security, Data analysis}
	\resumeSubItem{Languages}{~~~~~~~~~~ C, C++, Java, Python, Golang, HTML, PHP, JavaScript, SQL, Bash, R}
	\resumeSubItem{Frameworks}{~~~~~~~~ Spring Boot, NodeJS, ReactJS, Flask, LAMP, NLTK, SpaCy, TensorFlow, Keras}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~~~~~ Kubernetes, Docker, Git, Wireshark, Vagrant, Jenkins, Anaconda, Jupyter notebook}
	\resumeSubItem{Platforms}{~~~~~~~~~~~ Linux, Web, MacOS, AWS, GCP, Azure}
	\resumeSubItem{Soft Skills}{~~~~~~~~~~~ Writing, Team work, Presentation, Time Management}
	\resumeSubItem{Sports \& Hobbies}{~Badminton, Table Tennis, Cricket, Yoga, Quizzing, Solving math puzzles}

\resumeSubHeadingListEnd
\vspace{-5pt}
\section{\faIcon{suitcase}~~Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{GoIbibo - A go-MMT group company}{Onsite}
    {Software Development Intern (Full-time)}{Jun 2018 - Aug 2018}
    \resumeItemListStart
        \resumeItem{Identification of fraudulent flight bookings}
          {Developed a Chrome extension using javascript to monitor and track down agents doing online booking frauds in call centers.}
          \resumeItem{GIA chat bot}
          {Built an automated chat conversation for availing a cab voucher and booking a heli taxi to the airport. GIA is a Goibibo built Intelligent chat system.}
      \resumeItemListEnd
\vspace{-3pt}
    \resumeSubheading
		{Walmart Global Technology Services India Pvt. Ltd.}{Onsite}
		{Summer Intern (Full-time)}{May 2019 -  Jul 2019}
		\resumeItemListStart
        \resumeItem{\color{blue}\href{https://github.com/cloudmarker/cloudmarker}{Cloudmarker}}
          {Contributed to the Cloudmarker open source project, which is a framework used for cloud monitoring and auditing. Developed the plugin for auditing of GCP cloud environments.}
        \resumeItem{Risk score}
          {Worked on integrating a ML model which used clustering techniques to categorize security misconfigurations and generate a risk score.}
		\resumeItemListEnd
\vspace{-3pt}
    \resumeSubheading
		{Walmart Global Technology Services India Pvt. Ltd.}{Onsite/Remote}
		{Software Developer (Full-time)}{Jan 2020 -  Present}
		\resumeItemListStart
		\item\small{Started as a 6 month intern in Walmart InfoSec team, converted to a full time employee starting Aug 2020 in the InfoSec Development team}
		\item\small{Worked on design and development of features for an internal \textbf{vault for secrets management}.}
		\item\small{Contributed to development of features for internal \textbf{password sharing and credential management} tool.}
		\item\small{Had the unique opportunity to work with proprietary software used in \textbf{Walmart payment gateways} for credit card and cvv detail encryption/decryption with format preserving encryption.}
		\item\small{Involved in design and development of a service for \textbf{certificate lifecycle management}, which facilitates manual and auto renewal of certificates on Walmart loadbalancers.}
		\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{\faIcon{laptop}~~Projects}
\resumeSubHeadingListStart
\projectSubheading
    {\color{blue}\href{https://bit.ly/2Zm3BBc}{Explore using of ML models for replacing Database Indexes \footnotesize{\faIcon{link}}}}{Research Project}
    {Database, Hierarchical models, Neural networks, B+ Trees, Indexes}{Aug 2019 - Dec 2019}
\resumeItemListStart
\item\small{Explored using machine learning models to replace database index structures, which exist in the form of B+Trees.}
\item\small{Worked with Cassandra DB, experimented with various learned models to learn the data storage patterns and make prediction on the location of a given record}
\item\small{The learned models reduced the additional storage required for indexes and also reduced the time required to make database queries.}
\resumeItemListEnd
\vspace{2pt}
\projectSubheading
    {\color{blue}\href{https://bit.ly/3lbhVUZ}{Recommendation system for agriculture \footnotesize{\faIcon{link}}}~~~\href{https://github.com/jaibhageria/Agrolyzer}{\footnotesize{\faGithub} Code}~~~\href{https://youtu.be/-an0M1r3MrM}{\footnotesize{\faIcon{youtube} Video}}}{Personal Project}
    {Precision agriculture, Neural networks, Time series analysis, Supervised learning}{Oct 2018 - Dec 2018}
\resumeItemListStart
\item\small{Developed a recommendation engine to suggest farmers with the correct crops they should plant looking at various factors like land area, weather patterns and crop season.}
\item\small{Used neural networks to predict crop production and time series analysis for predicting weather patterns. Recommendation to plant a crop was given based on estimated production and predicted weather.}
\resumeItemListEnd
\vspace{4pt}
\projectSubheading
    {{Indian Cricket league prediction model}~~~\color{blue}\href{https://github.com/jaibhageria/IPLPredictor}{\footnotesize{\faGithub} Code}}{Personal Project}
    {Tools used: Apache Spark MLLib, Scala, PySpark}{Sep 2018 - Nov 2018}
\resumeItemListStart
\item\small{Developed a score-wicket prediction model using Apache Spark MLlib to simulate the outcomes of Indian Premium League cricket matches during 2018 season.}
\item\small{Ball-by-ball data from previous matches was used to develop two simulation models - Bayesian probability-based and Decision tree-based.}
\resumeItemListEnd
\vspace{2pt}
\projectSubheading
    {{Container Orchestration}~~~\color{blue}\href{https://github.com/jaibhageria/ContainerOrchestrator}{\footnotesize{\faGithub} Code}}{Personal Project}
    {Tools used: Docker, Amazon Web Services - EC2 and AWS Load balancer}{Jan 2019 - Mar 2019}
\resumeItemListStart
\item\small{Developed a container orchestrator similar to Kubernetes, that can perform load balancing, fault tolerance, and auto-scaling.}
\item\small{The orchestrator engine ran successfully inside the Acts EC2 instance and load balanced all HTTP incoming requests equally to every Acts container}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-5pt}
\section{\faIcon{file-alt}~~Publications \& Conferences}
\resumeSubHeadingListStart
\resumeSubItem{Research paper: \color{blue}\href{https://link.springer.com/chapter/10.1007/978-981-15-9774-9_68}{Graph-Assisted Attention for Path Finding in Question Answering Task}~\footnotesize{\faIcon{link}}}{}
\resumeItemListStart
\item\small{Paper was published in \textbf{Emerging Technologies in Data Mining and Information Security} (a Springer publication) on pages 735-748 on 5th May 2021.}
\item\small{Used knowledge graphs to answer multi-hop type, path finding based questions from the babI dataset.}
\item\small{Tech: NLP, Neural networks, End to end memory networks, Dynamic memory networks, Knowledge graphs.}
\resumeItemListEnd
\vspace{2pt}
\resumeSubItem{Conference: IEMIS-2020, a Springer AISC conference~~\color{blue}\href{https://bit.ly/3FJkaq8}{Certificate}~\footnotesize{\faIcon{link}}}{}
\resumeItemListStart
\item\small{The \textbf{2nd International Conference on Emerging Technologies in Data Mining and Information Security} was held from 2nd - 4th July, 2020 in Kolkata, India. The theme was Data mining, Machine learning, IoT and Information Security}
\item\small{Presented this {\color{blue}\href{https://bit.ly/3xnp758}{research paper}} during the conference.}
\resumeItemListEnd
\vspace{2pt}
\resumeSubItem{Conference: IEEE CCEM 2020, Pre-Conference workshop}{}
\resumeItemListStart
\item\small{The \textbf{IEEE International Conference on Cloud Computing in Emerging Markets (CCEM) Pre-Conference Workshop} was held on 29th February 2020 in Bangalore, India.}
\item\small{Presented this {\color{blue}\href{https://bit.ly/2Zm3BBc}{research paper}} during the conference and received valuable feedback from professionals and academics.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-5pt}
%-----------Awards-----------------
\section{\faIcon{trophy}~~Honors \& Awards}
\begin{description}[font=$\bullet$]
\item{~~~~Awarded with the \textbf{CNR Rao Merit Scholarship for 7 semesters in PES University} for excellent performance in academics and being in top 20\% of the Computer Science batch.}
\vspace{-5pt}
\item {~~~~Finished at the \textbf{third place in CTF competition} organised by ISFCR (Center for Information Security, Forensics and Cyber Resilience) PES University on 27th July 2019.}
\vspace{-5pt}
\item {~~~~Completed \textbf{Github Hacktober Fest 2019} successfully. Contributed to 4 open source projects.}
\vspace{-5pt}
\item {~~~~Qualified for Grand finale of \textbf{SynerGE presents HACK'E'LTH 2019} organised by GE from 19th-20th September 2019 at Bangalore, India. Finished amongst the top 10 teams all over India.}
\vspace{-5pt}
\item {~~~~Successfully completed the \textbf{Crio Launch 2021 Student Developer program} from 31st Jan 2020 - 10th Apr 2020. Link to my project profile is {\color{blue}\href{https://criodo.github.io/Crio-Launch-Feb-2020-jai-bhageria/}{here}} and the certificate is {\color{blue}\href{https://raw.githubusercontent.com/CrioDo/Crio-Launch-Feb-2020-jai-bhageria/gh-pages/static/media/Crio-Launch-Feb-2020-Certificate.png}{here}}.}
\vspace{-5pt}
\item {~~~~Won \textbf{first place in In-QUIZ-itives 2021}, a tech quiz organised by Walmart in June 2021.}
\vspace{-5pt}
\item {~~~~Finished at the \textbf{first place in Core NetWars CTF tournament} organised by SANS \& Walmart in October 2021.}
\end{description}
\end{document}
